### 2018-12-22 Sections/quantum_algorithms.tex
sampling

Countless other quantum sampling problems have been described. Most notably, the IQP (instantaneous quantum protocol)\index{Instantaneous quantum protocol (IQP)} sampling problem is a very simple prescription for a quantum algorithm that has been shown to likely be classically hard \cite{bib:BremnerIQP}.

>>>>

Countless other quantum sampling problems have been described. Most notably, the IQP (instantaneous quantum protocol)\index{Instantaneous quantum protocol (IQP)} sampling problem is a very simple prescription for a quantum algorithm that has been shown to likely be classically hard despite having very shallow circuit depth and all-commuting gates \cite{bib:BremnerIQP}.
